Action Groupoids and Fractional Types

### 2016-06-19 pibackground.tex
sec 5.1 help

%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Operational Semantics and the Order of 1-Combinators}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Operational Semantics and the Order of 1-Combinators}
\label{sec:pisem}

@@

\begin{definition}[Power of a permutation]
  The $k^{th}$ power of a 1-combinator $p : \tau \iso \tau$, for
  $k \in \Z$ is
  \[
    p^k =
  \begin{cases}
    \idiso & k = 0 \\
    p \odot p^{k - 1} & k > 0 \\
    (!~p) \odot p^{k + 1} & k < 0 \\
  \end{cases}
  \]
\end{definition}

\begin{definition}[Order of a permutation]
  The order of a 1-combinator $p : \tau \iso \tau$, $\ord{p}$, is the
  least postitive natural number $k \in \N^+$ such that
  $p^k \isotwo \idiso$.
\end{definition}

% \begin{lemma}
%   Every $p : \tau \iso \tau$ has an order.
% \end{lemma}

% \begin{proof}
%   By cases.
%   \begin{enumerate}
%   \item $\ord{\idiso} = 1$
%   \item $\ord{\swapp} = \ord{\swapt} = 2$
%   \item $\ord{p_1 \odot p_2} = ???$
%   \item $\ord{p_1 \oplus p_2} = \ord{p_1 \otimes p_2} = \mathsf{lcm}(\ord{p_1}, \ord{p_2})$
%   \end{enumerate}
% \end{proof}

\begin{lemma}
  For $p : \tau \iso \tau$, $n \in \Z$, $p^{k + n} \isotwo p^n$ where
  $k = \ord{p}$.
\end{lemma}

\begin{proof}
  Trivial.
\end{proof}
